The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
some notes in section 5, but no editing yet

@@

>>>>

\rachel{Here is one thing that is still missing from the results
  section.  We had discussed a number of times lumping the galaxies
  together into slices with larger $\Delta z$ and showing that the
  trends in the shape distributions disappear.  You had shown me plots
  and numbers for these, but they don't seem to have gone into the
  paper.  Please include them, because it would be useful to be able
  to give some guidance on how wide the redshift slices should be to
  avoid this issue.}

@@

\rachel{Note to self: mention UDF, and tie back to bias in shear
  estimates?  Also, tie back to flux-limited samples, and why we
  should care about these results for them.}
